### 2014-05-03 remy-rebuttal.txt

We thank the reviewers for their detailed and thoughtful feedback.

Reviewer A: We agree that the sec-5.5 results on these RemyCCs when
run concurrently vs. CUBIC/Compound aren't great, but emphasize that
they weren't yet trained to compete with "buffer-filling" TCPs. When
we train against possible buffer-filling cross-traffic, we expect to
demonstrate throughput gains. Please note: CUBIC isn't fair to Newreno
or Compound either.

Reviewer B: We agree with the suggestion to cite Chiu/Jain, who found
that among linear schemes where flows start at the same time with
uniform RTT and last forever, AIMD converges to fairness. RemyCCs
aren't necessarily linear. Beyond [42], we don't know of a theoretical
treatment with these assumptions removed, but our work can give
feasibility results.

We also seek intuition about why RemyCCs do well. The short answer is:
they can switch between pacing and window-based control, and respond
quickly to entry/exit of flows.  We can now trace executing RemyCCs
and could expand the explanation.

Reviewer C:

1. Remy is intended solely for *offline* creation of
congestion-control schemes, which then run at the sender (top-right of
pg. 2; fig. 1; sec. 4.3). Connections start immediately.

2. Remy doesn't assume network paths are fixed. We evaluated on traces
of time-varying Verizon and AT&T LTE networks (figs. 6-8), with actual
flow lengths (fig. 3). Only in *offline training* did we use a mean
on/off time of 5 seconds. (Training parameters are on pg. 7, right
column; evaluation scenarios are under "Topologies.") Other reported
simulation results varied cross traffic, RTT, etc.

3. The network model used for training captures a 64-fold *range* of
BDP-per-user. We evaluated on networks inside and outside this range
(pg. 7, col. 2).

4. Re: XCP, it is *XCP* that needs to know the exact throughput of the
bottleneck link (footnote 8). Remy does not.

5. Remy doesn't assume the exact traffic model is provided; we trained
on a model but evaluated on a real (untrained) flow-length
distribution.

6. We don't claim Remy is optimal; there is an optimal scheme in
principle (sec 4.1), which we attempt to approximate. Section 3.3
stresses that the utility function is a tool used to design
protocols. It need not capture users' "true" utilities (cf. remarks in
Related Work re: stochastic NUM [42]).

7. The evaluation looked at more than just queueing latency. Our
tables (sec. 1) and charts (figs. 4-7,9) show delay-vs-throughput and
delay-fairness and throughput-fairness (shaded ovals).

### 2014-05-03 sprout_intro.tex
Import Remy

\section{Introduction}
\label{s:intro}

@@

%\paragraph{Summary of results.}
We conducted a trace-driven experimental evaluation (details in
\S\ref{s:eval}) using data collected from four different commercial
cellular networks (Verizon's LTE and 3G 1xEV-DO, AT\&T's LTE, and
T-Mobile's 3G UMTS). We compared Sprout with Skype, Hangout, Facetime,
and several TCP congestion-control algorithms, running in both
directions (uplink and downlink).

The following table summarizes the average relative throughput
improvement and reduction in self-inflicted queueing
delay\footnote{This metric expresses a lower bound on the amount of
  time necessary between a sender's input and receiver's output, so
  that the receiver can reconstruct more than 95\% of the input
  signal. We define the metric more precisely in \S\ref{s:eval}.} for
Sprout compared with the various other schemes, averaged over all four
cellular networks in both directions. Metrics where Sprout did not
outperform the existing algorithm are highlighted in red:

>>>>

\section{Introduction}
\label{sprout:intro}

@@

%\paragraph{Summary of results.}
We conducted a trace-driven experimental evaluation (details in
\S\ref{sprout:eval}) using data collected from four different commercial
cellular networks (Verizon's LTE and 3G 1xEV-DO, AT\&T's LTE, and
T-Mobile's 3G UMTS). We compared Sprout with Skype, Hangout, Facetime,
and several TCP congestion-control algorithms, running in both
directions (uplink and downlink).

The following table summarizes the average relative throughput
improvement and reduction in self-inflicted queueing
delay\footnote{This metric expresses a lower bound on the amount of
  time necessary between a sender's input and receiver's output, so
  that the receiver can reconstruct more than 95\% of the input
  signal. We define the metric more precisely in \S\ref{sprout:eval}.} for
Sprout compared with the various other schemes, averaged over all four
cellular networks in both directions. Metrics where Sprout did not
outperform the existing algorithm are highlighted in red:

### 2014-05-03 sprout_limit.tex
Import Remy

Although our results are encouraging, there are several limitations to
our work. First, as noted in \S\ref{s:problem} and \S\ref{s:sprout},
an end-to-end system like Sprout cannot control delays when the
bottleneck link includes competing traffic that shares the same
queue. If a device uses traditional TCP outside of Sprout, the
incurred queueing delay---seen by Sprout and every flow---will be
substantial.

>>>>

Although our results are encouraging, there are several limitations to
our work. First, as noted in \S\ref{sprout:problem} and \S\ref{s:sprout},
an end-to-end system like Sprout cannot control delays when the
bottleneck link includes competing traffic that shares the same
queue. If a device uses traditional TCP outside of Sprout, the
incurred queueing delay---seen by Sprout and every flow---will be
substantial.

### 2014-05-03 sprout_problem.tex
Import Remy

%\section{Cellular Wireless Videoconferencing: Context and Challenges}
\section{Context and Challenges}
\label{s:problem}

@@

The high delays in cellular wireless networks cannot simply be blamed
on bufferbloat, because there is no single buffer size that will
always work. It is also not simply a question of using an appropriate
Active Queue Management (AQM) scheme, because the difficulties in
picking appropriate parameters are well-documented and become harder
when the available rates change quickly, and such a scheme must be
appropriate when applied to all applications, even if they desire bulk
throughput. In \S\ref{s:eval}, we evaluate CoDel~\cite{CoDel}, a
recent AQM technique, together with a modern TCP variant (Cubic, which
is the default in Linux), finding that on more than half of our tested
network paths, CoDel slows down a bulk TCP transfer that has the link
to itself.
%CoDel dramatically improved TCP's
%end-to-end delays compared with a gateway that indefinitely queues
%packets, but not as much as Sprout (even without active queue
%management).
%
%Sprout outperformed Cubic-over-CoDel in delay (with a 60\% reduction)
%but also had 30\% less throughput. Sprout-EWMA surpassed
%Cubic-over-CoDel in throughput (by 31\%) and nearly matched it in
%delay.

@@

Our experimental results show that previous work (see
\S\ref{s:related}) does not address these challenges
satisfactorily. These methods are reactive, using packet
losses, round-trip delays, and in some cases, one-way delays as the
``signal'' of how well the network is doing. In contrast, Sprout uses
a different signal, the observed arrival times of packets at the
receiver, over which it runs an inference procedure to make
forecasts of future rates. We find that this method produces a good
balance between throughput and delay under a wide range of
conditions.

>>>>

%\section{Cellular Wireless Videoconferencing: Context and Challenges}
\section{Context and Challenges}
\label{sprout:problem}

@@

The high delays in cellular wireless networks cannot simply be blamed
on bufferbloat, because there is no single buffer size that will
always work. It is also not simply a question of using an appropriate
Active Queue Management (AQM) scheme, because the difficulties in
picking appropriate parameters are well-documented and become harder
when the available rates change quickly, and such a scheme must be
appropriate when applied to all applications, even if they desire bulk
throughput. In \S\ref{sprout:eval}, we evaluate CoDel~\cite{CoDel}, a
recent AQM technique, together with a modern TCP variant (Cubic, which
is the default in Linux), finding that on more than half of our tested
network paths, CoDel slows down a bulk TCP transfer that has the link
to itself.
%CoDel dramatically improved TCP's
%end-to-end delays compared with a gateway that indefinitely queues
%packets, but not as much as Sprout (even without active queue
%management).
%
%Sprout outperformed Cubic-over-CoDel in delay (with a 60\% reduction)
%but also had 30\% less throughput. Sprout-EWMA surpassed
%Cubic-over-CoDel in throughput (by 31\%) and nearly matched it in
%delay.

@@

Our experimental results show that previous work (see
\S\ref{sprout:related}) does not address these challenges
satisfactorily. These methods are reactive, using packet
losses, round-trip delays, and in some cases, one-way delays as the
``signal'' of how well the network is doing. In contrast, Sprout uses
a different signal, the observed arrival times of packets at the
receiver, over which it runs an inference procedure to make
forecasts of future rates. We find that this method produces a good
balance between throughput and delay under a wide range of
conditions.
